Continuous Generalization of Buildings

### 2017-06-16 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
defined some parameters for building growing

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

@@

\newcommand{\myabstract}{We proposed a method to continuous 
generalization of buildings from a start scale to a goal scale. 
%
For each building at the start scale, we generate its 
generalized form at 
the goal scale by enlarging and simplifying. Then we grow the  
building to the 
generalized form to realize continuous transformation. During 
the 
growing, we aggregate two buildings once they become too close 
to each other. We generate a new generalized form at the goal 
scale for 
the aggregated building so that we can continue growing.
%
After finishing the growing, we take the goal scale as the 
start scale and repeat our continuous generalization. The start 
scale and the target scale should not be too far away because we 
want the intermediate results to be somewhat simplified.

Our contribution is as follows. First, the buildings 
are enlarged continuously and at the same time are simplified. 
Second, the distance between each pair of two buildings is 
always larger than a specified distance. Third, there is no thin 
part in our results.}

@@

Elimination
If every building should have area 4d2at least, we buffer 
buildings with radius xd (x<2). After the buffering, some too 
small buildings will be eliminated. The small buildings which 
manage to merge with other buildings may survive. The eliminated 
buildings should not participate in next buffering step, which 
uses larger d.

@@

@@

>>>>

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage[size=small,labelfont=bf]{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
% \newcommand{\ml}{\ensuremath{M_+}\xspace}
% \newcommand{\ms}{\ensuremath{M_-}\xspace}

@@

\newcommand{\myabstract}{We proposed a method to continuous 
	generalization of buildings from given start scale to any smaller goal 
	scale. 
	%
	If several buildings are close to each other at the start 
	scale, we bridge them by line segments and take the merge of these 
	buildings 
	and bridges as one building.
	For each building, either an original one or a merged one, at the start 
	scale, 
	we generate its target shape at 
	the goal scale by enlarging and simplifying. Then we grow the  
	building to the target shape. 
	%
	After finishing the growing, we take the goal scale as the 
	start scale and repeat our continuous generalization.
	\newline\indent
	Our contribution is as follows. First, the buildings 
	are enlarged continuously. At the same time, they are simplified. 
	Second, we ensure that the distance between any pair of two buildings is 
	always larger than a specified threshold.}

@@

Elimination
If every building should have area $4d^2$at least, we buffer 
buildings with radius $xd$ (x<2). After the buffering, some too 
small buildings will be eliminated. The small buildings which 
manage to merge with other buildings may survive. The eliminated 
buildings should not participate in next buffering step, which 
uses larger d.

@@

\section{Method}

If several buildings are close to each other at the start 
scale, we bridge them by line segments and take the merge of these 
buildings 
and bridges as one building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. Then we grow the  
building to the target shape. 
%
After finishing the growing, we take the goal scale as the 
start scale and repeat our continuous generalization.
\newline\indent
Our contribution is as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.

If we grow a building with radius $d_\mathrm{G}$, some part of a building will 
grow at most $2d_\mathrm{G}$.
The length of a bridge can be as large as
\begin{equation}
\label{eq:BridgeLength}
l_b=4d_\mathrm{G}+d_\epsilon.
\end{equation}
\todo[inline]{$d_\mathrm{G}$ or $D_\mathrm{G}$?}

\subsection{Parameters for growing}
The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
($S_\mathrm{g}>S_\mathrm{s}$).
The area of a building should be larger than $a$ mm$^2$ on a map.
A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ mm.
Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm in order to survive.
In order to eliminate some small buildings, we define our growing distance as
\begin{equation}
\label{eq:d_G}
	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is our growing factor. A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.

\begin{figure}[tb]
	\centering
	\includegraphics{Growth}
	\caption{Growth.}
	\label{fig:Growth}
\end{figure}

The distance between two buildings should be larger than a threshold, say, 
$\epsilon$ mm on map \parencite{Stoter2009}.
In order to make the shape of a building simpler, we simplify buildings 
using the Douglas--Peucker algorithm \parencite{Douglas1973} with preservation 
of right angles.
To avoid using too many thresholds, we also use $\epsilon$ mm for the 
simplification algorithm, hence the real threshold distance 
is
\begin{equation}
\label{eq:d_epsilon}
d_\epsilon= \epsilon  S_\mathrm{g}.
\end{equation}

If we insist on that we should observe 
the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
sure that
\begin{equation}
\label{eq:a_limit}
\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
\end{equation}
Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
\begin{equation}
a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
\end{equation}
\textcite{Stoter2009} used $0.2$ mm as minimal distance between two buildings 
on a map. We set our $\epsilon=0.2$.
We also require 
that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
On one hand, we should have a large $x$ so that we will see the 
growing most of the time.
On the other hand, we wish to keep bridges short as bridges are intrusions to 
our map, which means we should have a small $x$ and a large $\lambda$ so that 
we will have a small 
$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
$\lambda$ as our $a$ is already much larger than $0.16$ mm$^2$ on 
map, which is the area limit used by \textcite{Stoter2009}. As a result, we set 
$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
Using these setting, we have
\begin{equation}
a \ge 4.
\end{equation}
according to Eq.~\ref{eq:a_limit}.

Therefore, we may grow up to distance 
\[
D_\mathrm{G} = d_\mathrm{G} + d_\epsilon.
\]
Fig.~\ref{fig:ExtraGrowth} shows such an enlargement and simplification, where  
variable $d_\mathrm{e} (\le d_\epsilon)$ is the extra growing distance.

A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
A hole has area 
slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
growing with 
distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
unless the 
area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
that we do 
not fill a hole even if the hole has a large area because a large hole may be 
split into several small holes by filling. 
Although our intermediate results may violate the rule that a hole should be at 
least some size, we try to avoid the violation for a map at a goal scale.
\textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is at 
least $8$ mm$^2$ on the map. Following their setting, we wish to have $\pi 
D_\mathrm{G}^2 \ge 8 S_g^2$.

Now we discuss how to set the parameters according to our requirements. First, 
we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
grow $d_\mathrm{G}$. Only a small part will continue growing after the building 
has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
time, we want to have a large $d_\mathrm{G}/d_\epsilon$.

We cannot fulfill all the requirements.

\begin{figure}[tb]
	\centering
	\includegraphics{ExtraGrowth}
	\caption{In the left figure, the green polygon represents a building, and 
	the dashed polygon is the enlargement of the building. In the right 
	figure, the dashed polygon has been simplified to a rectangle. In order to 
	fill the rectangle, most parts of the (green) building needs to grow 
	distance $d_\mathrm{G}$, but the pit needs to grow $d_G + d_\mathrm{e}$, 
	where $d_\mathrm{e}$ is the extra growing distance.}
	\label{fig:ExtraGrowth}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{GrowingExample}
	\caption{GrowingExample.}
	\label{fig:GrowingExample}
\end{figure}

@@

We our intermediate results may violate more cartographic rules, but we try to 
make the results at goal scales violate as few rules as possible.

Ideally, for a rectangle, the ratio of width to height should be kept.

\todo[inline]{consider multi bridges; consider transparency of bridges in stead 
of enlarging}
